\documentclass[letterpaper]{article}
\usepackage{geometry}
\geometry{
	left = 1in,
	right = 1in,
	top = 1in,
	bottom = 1in
}


\begin{document}

\noindent
Oliver Evans \\
Intro to Numerical Python \\
\today \\

\section{Sample Problems}
\begin{enumerate}
	\item Stock Market Data
	\begin{itemize}
		\item Find stock data for Google, Apple, and Microsoft for the last 6 months  
			\begin{itemize}
				\item try \textit{finance.yahoo.com}
			\end{itemize}
		\item Save data in a Pandas DataFrame
		\item Use Numpy to calculate derivatives
		\item Plot stocks and derivatives using matplotlib/seaborn
	\end{itemize}
\item Symbolic Taylor Series
	\begin{itemize}
		\item Construct a function $TS(f,a,n)$ which returns the $nth$ partial sum of the Taylor series for $f$ about $n$
		\item If you're feeling brave, try to make an interactive plot with a slider for n
	\end{itemize}

\item Musical Scales
	\begin{itemize}
		\item Create a Numpy array of a sine wave with amplitude 1 with a lot of samples
		\item Use scikits-audiolab to play the sound
		\item Experiment with other mathematical functions. What do they sound like?
		\item Generate an A major scale based on A=440Hz with each note lasting 1 sec.
		\item Repeat with antique musical scales (Just intonation, Pythagorean)
	\end{itemize}
    
\item Compare with MATLAB / Mathematica / Fortran
	\begin{itemize}
		\item What advantages/disadvantages does Python have?
		\item Ease of coding?
		\item Speed?
		\item Language Features?
		\item Documentation/community?
	\end{itemize}

\item Look at some cool notebooks
	\begin{itemize}
		\item Google \textit{jupyter gallery of interesting IPython Notebooks}
		\item Read through some interesting looking notebooks
		\item Do you notice any interesting Python features?
		\item Any Python syntax that you don't understand?
	\end{itemize}

\item Explore Python Packages
	\begin{itemize}
		\item Scikits: \textit{https://scikits.appspot.com/scikits}
		\item Numeric/Scietific: \textit{https://wiki.python.org/moin/NumericAndScientific}
	\end{itemize}
    
\end{enumerate}

\end{document}
